---
title: "Why I am always right about movies"
output: pdf_document

---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5)

options(dplyr.summarise.inform=F)

if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(knitr)

list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

# Data loading:
    Loc <- "data/Movies/"
    movies <- read_csv(glue::glue("{Loc}Movies.csv"))


```


# Overview

In this report, we look at movies and why my friend is mostly wrong.

## Rotten Tomatoes vs audience scores

If we look at the audience scores compared to ROtten Tomatoes, we see that the frequency 

```{r}
 right <- freq(movies)

 kable(right)
```
In general we can see that the audience and Rotten Tomatoes tend to score in the same range for the same movie: 

```{r}
g <-plot_movies(movies, xaxis_size = 5, xaxis_rows = 3)
g

```


### Profitability


If we calculate the average profitability of all the studios, we see that Disney has the highest average.
```{r,  warning =  FALSE}

profit <-  profitability(movies)

kable(profit)


```
If we look at worlwide gross however, we see that Disney doesn't fair too badly, even though it is not the top.
```{r}
gross <- worldgross(movies)
kable(gross)
```

## Correlation

Using the Spearman's corrlation test we can see that the correlation between world wide gross and audience score is in fact 29% which is far below 80%.

```{r}
corr <- cor.test(x=movies$`Audience  score %`, y=movies$`Worldwide Gross`, method = 'spearman', exact = FALSE)
print(corr)

```

We could get a basic view from a scatter plot. Since the points are far from one another, we could already surmise that the correlation is weak.

```{r}
g <-corr_plot(movies, xaxis_size = 5, xaxis_rows = 3)
g

```




